\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-11-20 journalWallFriction/ReviewConditionalAccept/Response.tex

\NewDocumentCommand \Reviewer { m } {
	\stepcounter{reviewer}
	\subsection*{Comments~by~Reviewer~#1}
}

\begin{document}
	\letter{\emph{Exploiting Non-Slip Wall Contacts  to Position Two Particles Using The Same Control Input}}{IEEE Transactions on Robotics}

	\section*{Response to Reviewers}
	In the following document, we have provided detailed responses to the comments and questions of the reviewers. Comments and questions by reviewers are in \textcolor{blue}{blue}, our responses are in black.

	\emph{Comments by Associate Editor}
	\response{Both reviewers were pleased with the authors' revised manuscript. It is
the opinion of the Associate Editor that this paper will be publishable
in T-RO in some form. However, both reviewers have lingering concerns
about discrepancies between the purported contribution of the paper and
what is actually demonstrated. In the next draft of the manuscript, the
authors are encouraged to be explicit in making sure that the stated
contributions match what has been shown. This could involve removing or
softening certain claims, or adding new material to strengthen certain
claims.}

	We are grateful for the efforts of our reviewers.

	\Reviewer{\#1}\response{In the revised version most of my previous concerns have been
addressed.  I think with minor revisions the manuscript could be
suitable for publication. }
	Thank you! We have completed a minor revision, as explained below.

	\response{The remaining issue still comes back to whether the iterative procedure
is able to reach all target configurations.  The new manuscript shows
numerically that the accesible space approaches the entire space for a
circular 2D domain.  The paper, however, is meant to also cover any
convex domains.  Can the authors also prove that the accessible space
approaches the entire domain for any convex domain?  Or at least other
polygonal cases?   I see that on p4 in the last paragraph of section C,
there is a statement that particles can be steered to arbitrary
positions, but without an explanation of how that result is obtained,
which should be included.  I also think that paragraph should be
highlighted a little more by a section title (to be parallel with the
development of the circular workspace).  Assuming this can be explained
then I would be satisfied with the manuscript.}

	\Reviewer{\#2}
	\response{The authors did a great job in addressing my and the other reviewer's
comments in a set of meaningful changes to the manuscript, including
new analysis to investigate many of the questions. 
The only remaining comment is that the abstract and introduction imply
that 3D results are obtained in this work. While this is shown
theoretically, no 3D experimental results are shown. The abstract and
introduction should state this explicitly as this is viewed as a
notable limitation in what is actually demonstrated. }
	Thank you. We were pleased to get this review, because it led us to think more deeply on how to present the results and led to the major revisions detailed below.

### 2018-11-20 journalWallFriction/SwarmShapeControl.tex
made some work for Shiva, put all the text revision we think we need, except to refer to new Fig. 5

@@

Steered particles offer a method for targeted therapy, interventions, and drug delivery in regions inaccessible by large robots.
For example, magnetic actuation of particles has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).
 This paper investigates position control of particles using uniform forces (the same force is applied everywhere in the workspace).
Given a controllable field that can generate bidirectional forces in three orthogonal directions, steering one particle in 3D is trivial. 
Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
However, the walls of \emph{in vivo} and artificial environments often have surface roughness such that the particles do not move unless actuation pulls them away from the wall.
In previous work, we showed that the individual 2D position of two particles is controllable using global inputs in a square workspace with non-slip wall contact \cite{shahrokhi2017algorithms}.
Because \emph{in vivo} environments are usually not square, this paper extends the previous work to all convex workspaces and to 3D positioning. 
We investigate analytically an idealized variant of this problem with non-slip boundaries and control inputs that are applied uniformly to all particles in the workspace.
This paper also implements the algorithms using a hardware setup inspired by the gastrointestinal tract.

>>>>

\newcommand{\revision}[1]{
  \textcolor{Blue}{#1}
}

@@

Steered particles offer a method for targeted therapy, interventions, and drug delivery in regions inaccessible by large robots.
For example, magnetic actuation of particles has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).
 This paper investigates position control of particles using uniform forces (the same force is applied everywhere in the workspace).
Given a controllable field that can generate bidirectional forces in three orthogonal directions, steering one particle in 3D is trivial. 
Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
However, the walls of \emph{in vivo} and artificial environments often have surface roughness such that the particles do not move unless actuation pulls them away from the wall.
In previous work, we showed that the individual 2D position of two particles is controllable using global inputs in a square workspace with non-slip wall contact \cite{shahrokhi2017algorithms}.
Because \emph{in vivo} environments are usually not square, this paper extends the previous work to all convex workspaces, \revision{ and shows how this could be extended} to 3D positioning \revision{of neutrally buoyant particles.} 
We investigate analytically an idealized variant of this problem with non-slip boundaries and control inputs that are applied uniformly to all particles in the workspace.
This paper also implements the algorithms \revision{in 2D} using a hardware setup inspired by the gastrointestinal tract.

### 2018-11-20 journalWallFriction/intro.tex
Haoran's changes
made some work for Shiva, put all the text revision we think we need, except to refer to new Fig. 5

\section{Introduction}\label{sec:Intro}
Particle swarms propelled by an external field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}.
%
The small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a broadcast signal. 
 The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
  Consider a system of point-particles in a 2D, planar workspace.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm.
 Techniques are needed that can handle this underactuation.

@@

This paper is an elaboration of preliminary work in a conference paper \cite{shahrokhi2017algorithms} which considered only square workspaces. This work extends the analysis to convex workspaces and 3D positioning. This paper also implements the algorithms using a hardware setup inspired by the anatomy of the gastrointestinal tract.

>>>>

\section{Introduction}\label{sec:Intro}
Particle swarms propelled by an external field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}.
%
The small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a broadcast signal. 
 The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
  Consider a system of point-particles in a 2D planar workspace.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm.
 Techniques are needed that can handle this underactuation.

@@

This paper is an elaboration of preliminary work in a conference paper \cite{shahrokhi2017algorithms} which considered only square workspaces. This work extends the analysis to convex workspaces and 3D positioning. This paper also implements the algorithms \revision{in 2D} using a hardware setup inspired by the anatomy of the gastrointestinal tract.

### 2018-11-20 journalWallFriction/theory2robAlgs.tex
made some work for Shiva, put all the text revision we think we need, except to refer to new Fig. 5

% worst case analysis
 This algorithm allows two particles to be steered to arbitrary positions as long as the initial particle positions are separated by at least $\epsilon$, and at least one goal position is $\epsilon$ distance from a wall, where $\epsilon$ is a small, positive, user-defined number. 
For a square workspace where the length of each side is $L$, the worst case path length is $(\sqrt{2}+2)L$, and requires at most five moves (see Fig.~\ref{fig:shapeControlMathematica1}f).
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

>>>>

\subsection{\revision{Convex Workspaces: Accessible Region}}
% worst case analysis
 This algorithm allows two particles to be steered to arbitrary positions as long as the initial particle positions are separated by at least $\epsilon$, and at least one goal position is $\epsilon$ distance from a wall, where $\epsilon$ is a small, positive, user-defined number. 
For a square workspace where the length of each side is $L$, the worst case path length is $(\sqrt{2}+2)L$, and requires at most five moves (see Fig.~\ref{fig:shapeControlMathematica1}f).
As the corner angles increase, the number of moves required to access the entire configuration space increases.  \revision{For a circular workspace, with corner angles of 180$^\circ$, the worst case configuration can only be approached asymptotically, as explained in Section~\ref{sec:simulation}.}

\textcolor{red}{Insert figure 6 which shows the reachable delta config space for a square for 1,2,3,4,5 moves, maybe show two examples.}

% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,
